A warm sub-Neptune transiting a Solar twin in TESS

### 2019-09-24 paper/ms.tex
adding data
star name added
eccentricity calculations and paper outline

\include{preamble}

@@

\title{Title}

@@

@@

\author{Jacob L. Bean}
\affiliation{\chicago}

@@

\begin{abstract}\noindent
\todo{to be written}
% context
% aims
% methods
% results
\end{abstract}

\keywords{
something
---
science
}

@@

@@

\software{
%    \code{Astropy} \citep{astropy},
    \code{exoplanet} \citep{exoplanet},
    \code{IPython} \citep{ipython},
    \code{matplotlib} \citep{matplotlib},
    \code{numpy} \citep{numpy},
    \code{scipy} (\url{https://www.scipy.org/}),
}

% \facility{}

>>>>

\include{preamble}
\newcommand{\hoststar}{\acronym{HIP}\ 96160\xspace}

@@

\title{A warm sub-Neptune transiting a Solar twin in TESS}

@@

\author{Jhon Yana Galarza}
\affiliation{\USP}

@@

\author{Lorenzo Spina}
\affiliation{Monash}

%\author{Jacob L. Bean}
%\affiliation{\chicago}

@@

\begin{abstract}\noindent
% Precise characterization of exoplanet host stars is critical to our understanding of their properties. 
% However, stellar spectroscopic characterization can be plagued with 
% context
% aims
% methods
% results
\end{abstract}

\keywords{
}

@@

%The Transiting Exoplanet Survey Satellite (\TESS) has detected over one thousand candidate exoplanets to date. (blah blah)

%\hoststar has been studied extensively through a dedicated \RV planet search and spectroscopic abundance survey targeting solar twin stars. ...

\section(Data)
\label{s:data}

\subsection{Photometry}

(about \TESS photometry)

\subsection{Spectra}

(about \HARPS \RVs)

(about co-added spectrum - SNR etc)

\section{Analysis \& Results}
\label{s:analysis}

\subsection{Stellar Characterization}
\label{s:analysis:star}

(cite spectroscopic properties + abundances from previous work, plus Gaia DR2)
(isochrones fit - we use this mass \& radius going forward)

(attempts at seismology \& rotation period)

\subsection{Photometric Analysis}
\label{s:analysis:photometry}

\subsection{\RV Analysis}
\label{s:analysis:rvs}

\subsection{Joint Analysis}
\label{s:analysis:joint}

\section{Discussion}
\label{s:discussion}

(Low probability of background contaminants - discuss Gaia, spectra)

(reliability of the RV fit - potential for more planets? activity?)

(M-R diagram)

(prospects for further compositional analysis)

(prospects for atmospheric characterization)

\section{Conclusion}
\label{s:conclusion}

@@

\software{
    \code{Astropy} \citep{astropy},
    \code{exoplanet} \citep{exoplanet},
    \code{IPython} \citep{ipython},
    \code{matplotlib} \citep{matplotlib},
    \code{numpy} \citep{numpy},
    \code{scipy} (\url{https://www.scipy.org/}),
}

\facility{TESS, HARPS}
